A Classical Density-Functional Theory for Describing Water Interfaces

### 2013-08-20 papers/water-saft/paper.tex
another water paragraph from yesterday Tested everything on bingley.

>>>>

The classical density functional for water from
Reference~\citenum{hughes2013classical} consists of four terms:
\begin{align}
  F[n(\rr)] &= F_{\text{ideal}}[n(\rr)] + F_{\text{HS}}[n(\rr)]
  + F_{\text{disp}}[n(\rr)] + F_{\text{assoc}}[n(\rr)]
\end{align}
where $F_{\text{ideal}}$ is the ideal gas free energy and
$F_{\text{HS}}$ is the hard-sphere excess free energy, for which we
use the White Bear functional~\cite{roth2002whitebear}.
$F_{\text{disp}}$ is the free energy contribution due to the
square-well dispersion interaction.  The dispersion term of the free
energy contains one empirical parameter, which is used to fit the
surface tension of water near one atmosphere.  Finally,
$F_{\text{assoc}}$ is the free energy contribution due to association,
which is the term that we examine in this paper.
